---
title: "Regression"
author: "Haoyu Yue"
date: "2021/2/28"
output:
  html_document: default
  pdf_document: default
---

# Continuous Regression

### Import all packages and clean the environment

```{r}
library(haven)
library(tidyverse)
library(pander)
library(dplyr)
rm(list=ls())
```

### Import the data

```{r}
# 
data <- read.csv("https://raw.githubusercontent.com/Group8-GovAnalyticsProject/Merging/main/final_merged_data.csv")
```

### State the hypotheses

```{r}
# Hypothesis 1: Positive rate increases as median age larger.
hypo1=formula(precount_positive~median_age)
# Hypothesis 2: Positive rate increases as median age larger, income decreases.
hypo2=formula(precount_positive~median_age*median_hhold_inc)
```

### Build and compute the regression models

```{r}
model_1=glm(hypo1,
         data=data,
         family="gaussian")
model_2=glm(hypo2,
         data=data,
         family="gaussian")
```

### Read the result

*Result for model/hypotheses 1*

```{r}
pander(summary(model_1))
```

*Result for model/hypotheses 2*

```{r}
pander(summary(model_2))
```

*Compare the two models and find the better one*

```{r}
anova(model_1,model_2,test="Chisq")
```
Due to the p-value = 7.911e-12, these two models has statistical differences. And model 2 is better than model 1 because DF and residential are smaller. 

```{r}
RSquare_1 <- rsq::rsq(model_1,adj=T)
RSquare_2 <- rsq::rsq(model_2,adj=T)
```


### Summart plots

```{r}
library(dotwhisker)
library(ggplot2)
dwplot(model_2,by_2sd = F)
```

```{r}
persp(model_2)
```


# Binary Regression

There is no binary data in our data, so we would like to add a column called high_risk, which means the percent of positive is more than the median of it. 

```{r}
data$high_risk <- ifelse(data$precount_positive>median(data$precount_positive),1,0)
data$high_risk<-factor(data$high_risk)
```

### State the hypotheses

```{r}
# Hypothesis 3: High risk or not has relationship with median age.
hypo3=formula(high_risk~median_age)
# Hypothesis 4: High risk or not has relationship with median age and median income.
hypo4=formula(high_risk~median_age*median_hhold_inc)
```

### Build and compute the regression models

```{r}
model_3=glm(hypo3,
         data=data,
         family="binomial")
model_4=glm(hypo4,
         data=data,
         family="binomial")
```

### Read the result

*Result for model/hypotheses 3*

```{r}
pander(summary(model_3))
```

*Result for model/hypotheses 4*

```{r}
pander(summary(model_4))
```

*Compare the two models and find the better one*

```{r}
lmtest::lrtest(model_3,model_4)
```
Model_4 is chosen for this hypotheses.

### Get marginal effects

```{r}
library(margins)
(marginINFO = margins(model_4))
```

```{r}
(marginSUMM=summary(marginINFO))
```

### Get some plots

```{r}
base= ggplot(marginSUMM, 
             aes(x=factor, y=AME)) 
base= base + geom_point() 
 
plotMargins = base + theme(axis.text.x = element_text(angle = 80,size = 6,hjust = 1)) 
plotMargins +geom_errorbar(aes(ymin=lower, ymax=upper))
```



```{r}
persp(model_4)
```







